Assignment 2

### 2019-06-29 ex2/report/report.tex
Typos

When computing ALE plots, we experienced the problem of empty intervals. If there are intervals  that do not contain any values, the usual definition which takes values between the interval's boundaries for estimating the conditional probability density for feature values.

@@

\begin{table*}
\caption{Misclassified instances: \textit{false positives} shows the class of the attack sample that is closest to the misclassified benign sample; \textit{false negatives} shows how many attack samples of each class were falsely classified as benign.}
\label{tab:misclassified_instances}
\begin{tabular}{l l l l} 
\toprule 
Attack type & total number & false positives & false negatives \\
\midrule
Botnet:ARES  & 275 & 13 & 6 \\
Brute Force:FTP-Patator & 91 & 2 & 81 \\
Brute Force:SSH-Patator & 870 & 67 & 1 \\
DDoS:LOIT & 31887 & 0 & 29 \\
DoS / DDoS:DoS GoldenEye & 2490 & 2 & 1 \\
DoS / DDoS:DoS Hulk & 77998 & 4 & 1 \\
DoS / DDoS:DoS Slowhttptest & 1385 & 142 & 4 \\
DoS / DDoS:DoS slowloris & 1310 & 2 & 1 \\
DoS / DDoS:Heartbleed & 2 & 0 & 2 \\
Infiltration:Dropbox download & 25587 & 87 & 1783 \\
PortScan:PortScan - Firewall off & 53341 & 8 & 18 \\
PortScan:PortScan - Firewall on & 129 & 0 & 7 \\
Web Attack:Sql Injection & 6 & 0 & 1 \\
Web Attack:XSS & 233 & 69 & 100 \\
\bottomrule
\end{tabular}
\end{table*}

>>>>

When computing ALE plots, we experienced the problem of empty intervals. If there are intervals  that do not contain any values, the usual definition which takes values between the interval's boundaries for estimating the conditional probability density for feature values doesn't work.

@@

\begin{table*}
\caption{Misclassified instances of the first fold: \textit{false positives} shows the class of the attack sample that is closest to the misclassified benign sample; \textit{false negatives} shows how many attack samples of each class were falsely classified as benign.}
\label{tab:misclassified_instances}
\begin{tabular}{l l l l} 
\toprule 
Attack type & total number & false positives & false negatives \\
\midrule
Botnet:ARES  & 275 & 13 & 6 \\
Brute Force:FTP-Patator & 91 & 2 & 81 \\
Brute Force:SSH-Patator & 870 & 67 & 1 \\
DDoS:LOIT & 31887 & 0 & 29 \\
DoS / DDoS:DoS GoldenEye & 2490 & 2 & 1 \\
DoS / DDoS:DoS Hulk & 77998 & 4 & 1 \\
DoS / DDoS:DoS Slowhttptest & 1385 & 142 & 4 \\
DoS / DDoS:DoS slowloris & 1310 & 2 & 1 \\
DoS / DDoS:Heartbleed & 2 & 0 & 2 \\
Infiltration:Dropbox download & 25587 & 87 & 1783 \\
PortScan:PortScan - Firewall off & 53341 & 8 & 18 \\
PortScan:PortScan - Firewall on & 129 & 0 & 7 \\
Web Attack:Sql Injection & 6 & 0 & 1 \\
Web Attack:XSS & 233 & 69 & 100 \\
\bottomrule
\end{tabular}
\end{table*}
